---
output: 
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  collapse=TRUE,
  comment="#>",
  fig.path="man/figures/README-",
  fig.height = 7,
  out.width="100%"
)
# options(Encoding="UTF-8")
```

# {nih.joinpoint}

<!-- badges: start -->
[![Package-License](http://img.shields.io/badge/license-GPL--3-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html) 
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![CRAN status](https://www.r-pkg.org/badges/version/nih.joinpoint)](https://CRAN.R-project.org/package=nih.joinpoint)
[![Last Commit](https://img.shields.io/github/last-commit/DanChaltiel/nih.joinpoint/)](https://github.com/DanChaltiel/nih.joinpoint/)


## Joinpoint Regression Software

The package `{nih.joinpoint}` is an R interface to easily use National Institute of Health (NIH)'s 'Joinpoint Regression Software' v4.9.0.0.

> **Disclaimer**:  
> According to the [Terms of Use Agreement](https://surveillance.cancer.gov/joinpoint/callable/personal_joinpoint_agreement.doc) of NIH, I am not allowed to share a copy of the software   
> You need to apply at [https://surveillance.cancer.gov/joinpoint/callable/](https://surveillance.cancer.gov/joinpoint/callable/) to get your own copy. This package will **NOT** work otherwise.  
> If you want to cite this package in a publication, you have to cite NIH as well.

The software will come as a Windows installer that needs to be installed. If you cannot or don't want to install it in the default location ("C:/Program Files (x86)/Joinpoint Command/jpCommand.exe"), you should use `options(joinpoint_path="my/path/to/jp.exe")`.

This package comes with no guarantee that it will work for any other version than v4.9.0.0.

## Package Installation

As for now, you can only install the development version of this package from GitHub:

``` r
devtools::install_github("DanChaltiel/nih.joinpoint")
```

I plan to release it on CRAN someday.

```{r child="man/fragments/overview.Rmd"} 
```
