---
title: "Running a joinpoint analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running a joinpoint analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  # out.width = "100%",
  collapse = TRUE,
  comment = "#>"
)
```

The package `{nih.joinpoint}` is an R interface to easily use National Institute of Health (NIH)'s 'Joinpoint Regression Software' v4.9.0.0. 

This vignette assume that you applied at [https://surveillance.cancer.gov/joinpoint/callable/](https://surveillance.cancer.gov/joinpoint/callable/) to get your own copy of this software and installed it. If you cannot or don't want to install it in the default location ("C:/Program Files (x86)/Joinpoint Command/jpCommand.exe"), you should use `options(joinpoint_path="my/path/to/jp.exe")`.

This package will **NOT** work otherwise. Moreover, it comes with no guarantee to work for any other version than v4.9.0.0.


```{r child="../man/fragments/overview.Rmd"} 
```
