
The package `{nih.joinpoint}` is an R interface to easily use National Institute of Health (NIH)'s 'Joinpoint Regression Software' v4.9.0.0.

> **Disclaimer**:  
> According to the [Terms of Use Agreement](https://surveillance.cancer.gov/joinpoint/callable/personal_joinpoint_agreement.doc) of NIH, I am not allowed to share a copy of the software   
> You need to apply at [https://surveillance.cancer.gov/joinpoint/callable/](https://surveillance.cancer.gov/joinpoint/callable/) to get your own copy. This package will **NOT** work otherwise.  
> If you want to cite this package in a publication, you have to cite NIH as well.

The software will come as a Windows installer that needs to be installed. If you cannot or don't want to install it in the default location ("C:/Program Files (x86)/Joinpoint Command/jpCommand.exe"), you should use `options(joinpoint_path="my/path/to/jp.exe")`.

This package comes with no guarantee that it will work for any other version than v4.9.0.0.

## Dataset

This package includes a part of the sample dataset provided with the software:

```{r, fig.height = 3, fig.width=7, message=FALSE}
library(tidyverse)
library(nih.joinpoint)

sample_data %>% group_by(sex) %>% slice(1, 2, n()-1, n()) #first 2 and last 2 of each group

ggplot(sample_data, aes(x=year, y=rate, color=sex)) + geom_point() + geom_line()
```

## Parameters

You can use `run_options()` and `export_options()` to setup parameters for the joinpoint analysis:

```{r}
run_opt = run_options(model="ln", max_joinpoints=3, n_cores=3)
export_opt = export_options()
```

In this example, we ask for a log-linear model, with a maximum of 3 joinpoints to be found, using 3 cores of your processor to parallelize to computing. See `?run_options()` for more options.  
Export options are left as default as they often mess with the output, change them if you know what you are doing.

Note that the computing time will increase exponentially with `max_joinpoints` and will decrease with `n_cores`. 

## Run

To run the analysis, you then call `joinpoint()` with arguments: your dataset, the variables you want to consider, and the above-mentioned options.

```{r}
jp = joinpoint(sample_data, x=year, y=rate, by=sex, se=se,
               run_opt_ini=run_opt, export_opt_ini=export_opt)
names(jp)
```

Note that you can leave the options as default, and that the standard error can be left unfilled:

```{r eval=FALSE}
jp2 = joinpoint(sample_data, x=year, y=rate)
```

## Plotting

You can use `jp_plot()` to plot the joinpoint lines along the scatter points:

```{r, fig.height = 9, fig.width=7, message=FALSE}
jp_plot(jp) + patchwork::plot_layout(ncol=1)
```

The result is a [patchwork](https://github.com/thomasp85/patchwork/) of ggplots, as the legend must be different for every level.

## Logging

You can look at the logs using `cat()`:

```{r}
cat(jp$run_summary)
```
